Energy and the CES production function

### 2015-08-26 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Fixed residuals graph to match style of others.

  p <- ggplot() +
    geom_point(
      data=dataToPlot, 
      mapping=aes(
        x=Year, 
        y=Residuals, 
        fill=Model, 
        shape=Model, 
        size=Model #,
        # color=Inputs
        )
      ) +
    facet_grid(flavor ~ Country) +
    geom_hline(yintercept = 0, colour="gray50", size=0.1) +
    scale_x_continuous(breaks=c(1960, 1980, 2000)) +
    xlab("") +
    ylab("r") + 
    xy_theme() +
    labs(color = "Factors of production") # +
    # theme(legend.title=element_blank())

  model_points_style_quad(p)
}
@

>>>>

  ggplot() +
    geom_point(
      data=dataToPlot, 
      mapping=aes(
        x=Year, 
        y=Residuals, 
        fill=Model, 
        shape=Model, 
        size=Model
        )
      ) +
    facet_grid(flavor ~ Country) +
    geom_hline(yintercept = 0, colour="gray50", size=0.1) +
    scale_x_continuous(breaks=c(1960, 1980, 2000)) +
    xlab("") +
    ylab("r") + 
    xy_theme() +
    labs(color = "Factors of production") +
    # This is custom stuff here to match the model_points_style function. 
    # We can't use model_points_style, because the aesthetics are different here
    # with only two series (kl w/o CSP and (kl)e w/o CSP) in the graph.
    scale_size_manual(values = c(3, 3)) +
    scale_fill_manual(values = c("transparent", "transparent")) +
    scale_shape_manual(values = c(21, 23)) +
  theme(legend.title=element_blank())
}
@
